---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---



#  Data Preparation 
## library() calls
see groundhog_packages.R for more package setup
```{r setup, include=FALSE}
# load all required libraries using the groundhog package (installs libraries that are not installed yet)
source("load_packages.R")
```

## read eyetracking info
```{r}
data <- readRDS(here("output", "processed_data", "FacePrince_raw_eye_data.Rdata"))
```



## read trial  information 
```{r}
# side of presentation for each object
trial_info <- read_csv(here("data", "study_2_other_files", "facePrince_trial_info.csv")) %>%
  rename(trial_language = trial_lang)
```

## read participant info
```{r}
part_info <- readRDS(here("output", "processed_data", "anonymized_participant_info", "fp_part_info.Rdata"))
```





# participant exclusion
## premature birth
```{r}
part_info <- part_info %>%
  mutate(exclude_premature = case_when(
    gestation_weeks < 37 | gestation == "Prem" ~ 1,
    weight_in_grams < 2500 ~ 1,
    is.na(weight_in_grams) & is.na(gestation_weeks) ~ as.numeric(NA),
    TRUE ~ 0
  ))
```

## health 
```{r}
# to do
part_info <- part_info %>%
  mutate(exclude_health = NA)



part_info %>%
  distinct(health_comments, .keep_all = T) %>%
  select(part_id, health_comments) %>%
  write_csv(here("data", "study_2_other_files", "fp_health_to_check.csv"))
health_comments_checked <- read_csv(here("data", "study_2_other_files", "fp_health_checked.csv"))

part_info <- part_info %>%
  left_join(health_comments_checked %>% select(-health_comments)) %>%
  mutate(exclude_health = ifelse(exclude_health_comments == FALSE | is.na(health_comments), 0, 1))
```
## age
```{r}
### create age group variable

age_ranges <- read_csv(here("data", "age_ranges.csv"))


part_info <- part_info %>%
  mutate(age_group = as.double(str_extract(study_name, "[0-9]{1,2}"))) %>%
  left_join(age_ranges %>% select(age_group, min_age_continuous, max_age_continuous), by = "age_group")

part_info <- part_info %>%
  rowwise() %>%
  mutate(exclude_age = case_when(
    between(as.numeric(age_in_days), as.numeric(min_age_continuous), as.numeric(max_age_continuous)) ~ 0,
    TRUE ~ 1
  )) %>%
  ungroup() %>%
  select(-min_age_continuous, -max_age_continuous)
```


## language

```{r}
part_info <- part_info %>%
  mutate(exclude_language = case_when(
    lang_group == "none" ~ 1,
    !is.na(lang_group) ~ 0,
    TRUE ~ as.numeric(NA)
  ))
```

## prior study exclusions
by accident, FP18_P056 got scheduled after they already participated in LP. discussed with Krista that I won't exclude
```{r}
part_info <- part_info %>%
  mutate(exclude_priorStudy = 0) # no one gets excluded for this
```


## overview of participant exclusions
```{r}
part_info <- part_info %>%
  mutate(
    exclude_summary = case_when(
      exclude_priorStudy == 1 ~ "0_experimenterError", # should not have been scheduled
      exclude_age == 1 ~ "1_age",
      exclude_premature == 1 ~ "2_preterm",
      exclude_health == 1 ~ "3_health",
      exclude_language == 1 ~ "4_language",
      TRUE ~ "keeper"
    ),
    exclude = case_when(
      exclude_summary != "keeper" ~ 1,
      TRUE ~ 0
    )
  )

part_info %>%
  group_by(study, exclude_summary, lang_group) %>%
  count()
```
## remove unneccesary variables
```{r}
part_info <- part_info %>%
  select(
    -lang_percent_total, -starts_with("gestation"),
    -lang_group_by_lang, -starts_with("lang_exp_oth"), -starts_with("health"), -weight_in_grams
  )
```


# eyetracking dataframe prep



## add trial info
### create variables on trial info from soundfile name etc. 
```{r}
data <- data %>% rename(
  gaze_x = gaze_point_x_adc_spx,
  gaze_y = gaze_point_y_adc_spx,
  timestamp = recording_timestamp,
  order = studio_test_name
)
data %<>% mutate(
  attentiongetter = case_when(
    startsWith(as.character(data$media_name), "AttentionGetterGrey") ~ TRUE,
    TRUE ~ FALSE
  ),
  movie_name = case_when(
    attentiongetter == TRUE ~ "",
    grepl(".wmv", media_name) ~ str_remove(media_name, ".wmv")
  )
)


rev_lang <- function(language) {
  if (!language %in% c("Eng", "Fr")) {
    return(language)
  }
  result <- case_when(
    language == "Eng" ~ "Fr",
    language == "Fr" ~ "Eng"
  )

  result
}
data <- data %>%
  separate(movie_name,
    into = c("trial_speaker", "trial_lang_assigned_to_speaker", "trial_vid"),
    sep = "_",
    remove = F
  ) %>%
  mutate( # write out trial_speaker:
    trial_vid = tolower(trial_vid),
    speaker_gender = case_when(
      trial_speaker == "Male" ~ "man",
      trial_speaker == "Fem" ~ "woman"
    ),
    phase = factor(if_else(trial_vid %in% c("same", "switch"), "test", "familiarization")),
    trial_type = factor(if_else(phase == "test", trial_vid, NA_character_))
  ) %>%
  select(-trial_speaker)



# data %>% distinct(participant_name, trial_number, .keep_all = TRUE) %>%
#  select(phase, trial_type, fam_type, trial_lang, trial_speaker, movie_name) %>% View()
```

###  add info on trials
```{r}
# add info on which image is being seen

data <- left_join(data, trial_info,
  by = c("order", "movie_name")
)

data %>%
  group_by(is.na(trial_number), attentiongetter) %>%
  count()
```



## dealing with track loss
```{r}
data <- data %>% mutate(
  track_loss_reason =
    case_when(
      between(validity_right, 2, 4) | between(validity_left, 2, 4) ~ "validity is bad", is.na(gaze_y) ~ "no info on coord y",
      is.na(gaze_x) ~ "no info on coord x",
      between(gaze_x, 0, 1920) ~ "",
      between(gaze_y, 0, 1200) ~ "",
      gaze_x < 0 | gaze_x > 1920 ~ "outside of box",
      gaze_y < 0 | gaze_y > 1200 ~ "outside of box",
      TRUE ~ "not sure"
    ),
  track_loss = ifelse(track_loss_reason != "", TRUE, FALSE)
)
```

## add AOI info
AOI is full screen
```{r}
(aoi_info <- data.frame(
  target_side = "full_screen",
  L = 0, R = 1920, # left, right
  `T` = 0, B = 1200 # top, bottom
))


data <- add_aoi(data,
  aoi_info,
  x_col = "gaze_x",
  y_col = "gaze_y",
  aoi_name = "full_screen"
)
```


## check that data are on the right coordinate system
```{r}
# get rid of rows for attentiongetter &  where no video is presented
data <- data %>%
  filter(
    attentiongetter != TRUE,
    !is.na(media_name),
    media_name != ""
  ) %>%
  rename(gaze_y_tobii = gaze_y) %>%
  # Put GazePoint is on a cartesian coordinate system instead of Tobii system
  mutate(gaze_y = (gaze_y_tobii - 1200) * -1) %>%
  select(-gaze_y_tobii, -attentiongetter, -studio_project_name, -studio_event_data)
# the following code takes a bit to run
# check that there are no outliers left ( all gaze points are y:0-1200 and x 0-1900)
# with(data[data$track_loss==F,], plot(gaze_x, gaze_y)) #HK note: To me, the plot shows quite a few data points outside the range expected
```
## add info on participants with missing eyetracking data
```{r}
data <- data %>%
  mutate(has_eye_data = TRUE) # all participants in our dataframe have some kind of eyetracking data

participants_with_no_eye_data <- read_csv(here("data", "study_2_other_files", "fp_check_eye_data.csv"))



# merge missing data and eye_data_raw
data <- data %>%
  full_join(participants_with_no_eye_data, by = c("part_id", "has_eye_data"))
```




# Merge eyetracking data with participant info



## check whether participants are missing from either set
```{r}
missing_from_info <- data %>%
  distinct(part_id, .keep_all = T) %>%
  anti_join(part_info) %>%
  print()


missing_from_eyetracker <- part_info %>%
  distinct(part_id) %>%
  anti_join(data %>% distinct(part_id)) %>%
  arrange(part_id) %>%
  print()
```

## merge

```{r}
full_data <- full_join(data, part_info, by = "part_id")

# find matching mistakes
full_data %>%
  group_by(part_id, lang_group) %>%
  summarize(mean.en = mean(percent_english, na.rm = T)) %>%
  arrange(mean.en)
rm(data)
```

# eyetrackingR steps

## eyetrackingR preparations
```{r}
# delete duplicated rows (artifact introduced by tobii eyetracker)
full_data_dup_removed <- full_data %>%
  arrange(part_id, trial_number, timestamp, studio_event) %>%
  distinct(part_id, trial_number, timestamp, .keep_all = T)

data_eye_r <- make_eyetrackingr_data(full_data_dup_removed,
  participant_column = "part_id",
  trial_column = "trial_number",
  time_column = "timestamp",
  trackloss_column = "track_loss",
  aoi_columns = c("full_screen"),
  treat_non_aoi_looks_as_missing = FALSE
)


# check that no participants & trial are missing a moviestart & movieend message
full_data_dup_removed %>% # filter(!is.na(studio_event)) %>%
  group_by(part_id, media_name, studio_event) %>%
  count() %>%
  spread(studio_event, n) %>%
  filter(is.na(MovieEnd) | is.na(MovieStart))

# clean up df we don't need anymore
rm(full_data)
rm(full_data_dup_removed)
gc()
```

## rezero trials to beginning of trial

```{r}
# create a trial-specific timestamp (instead of timestamp relative to start of study)
data_rezero <- subset_by_window(data_eye_r,
  window_start_msg = "MovieStart",
  window_end_msg = "MovieEnd",
  msg_col = "studio_event",
  rezero = T
)
# need to rerun eyetrackingR because properties got lost?
data_rezero <- make_eyetrackingr_data(data_rezero,
  participant_column = "part_id",
  trial_column = "movie_name",
  time_column = "timestamp",
  trackloss_column = "track_loss",
  aoi_columns = c("full_screen"),
  treat_non_aoi_looks_as_missing = FALSE
)
```
# remove eyetracking data for videos that are longer

# calculate looking time 
## length of shortest video
it wasn't possible to make all videos same length, so we set the maximum looking time to the shortest length of any of the videos used
```{r}
video_lengths <- data_rezero %>%
  filter(phase == "test") %>%
  group_by(media_name) %>%
  summarize(max = max(timestamp))

shortest_video_length <- video_lengths %>%
  pull(max) %>%
  min(., na.rm = T)
```
## cap for each trial to shortest video length
capped at the shortest test video, then average

```{r}
data_rezero <- data_rezero %>%
  filter(timestamp <= shortest_video_length)
```



## save data for pupillometry analysis
need to do this before I remove participants for low looking in eyetracking, separate exclusion criteria there!
```{r}
data_rezero %>%
  select(
    study, part_id, gender, order, trial_number, exclude_summary, exclude,
    age_in_months, age_group,
    lang_group, percent_english, percent_french, percent_other, child_ethnicity, years_education,
    phase, fam_type, trial_type,
    gaze_x, gaze_y, validity_left, validity_right, pupil_left, pupil_right, full_screen, track_loss, track_loss_reason,
    speaker_gender, movie_name, timestamp
  ) %>%
  mutate(trial_number = as.numeric(as.character(trial_number))) %>%
  saveRDS(here("output", "processed_data", "fp_pupil_preprocessed.Rdata"))
```

# prepare data for eyetracking looking time analysis
## exclude trails with trackloss
```{r}
## Trackloss analysis

trackloss <- trackloss_analysis(data_rezero) %>%
  mutate(SamplesInAoi = Samples - TracklossSamples) %>%
  mutate(exclude_low_looking = ifelse(SamplesInAoi >= 60, 0, 1))

data_clean_all_subj <- data_rezero %>%
  left_join(trackloss %>% select(part_id, movie_name, exclude_low_looking)) %>%
  filter(exclude_low_looking != 1)
```
## check how many participants I have pre-removal

```{r}
data_clean_all_subj %>%
  distinct(part_id, .keep_all = TRUE) %>%
  group_by(study) %>%
  count(exclude_summary) %>%
  pivot_wider(names_from = study, values_from = n, values_fill = 0)
```

## get dataframe with only keepers for trail analysis
```{r}
data_clean_keepers <- data_clean_all_subj %>% filter(exclude_summary == "keeper")
```

## check if enough test trials for remaining participant
need at least 1 switch 1 same trial
```{r}
# check if enough data

drop_notenoughtrials <- data_clean_keepers %>%
  group_by(part_id, phase, trial_type) %>%
  distinct(trial_number, .keep_all = T) %>%
  count(.drop = F) %>%
  group_by(part_id) %>%
  mutate(exclude_notenoughtrials = case_when(
    min(n) < 1 ~ 1,
    length(n) < 3 ~ 1,
    TRUE ~ 0
  )) %>%
  arrange(-exclude_notenoughtrials)

# summarize which participants are excluded (get rid of diff rows for phase and trial type)
drop_notenoughtrials_merge <- drop_notenoughtrials %>%
  group_by(part_id) %>%
  summarize(
    exclude_trials = ifelse(sum(exclude_notenoughtrials) > 0, 1, 0)
  ) # if any exclusion reason present (either for fam or test, mark as 1 ie remove)

data_clean <- data_clean_all_subj %>%
  full_join(drop_notenoughtrials_merge) %>%
  mutate(
    exclude = case_when(
      exclude == 1 ~ exclude, # if was already excluded, no change
      exclude_trials == 1 ~ 1,
      TRUE ~ exclude
    ),
    exclude_summary = case_when(
      exclude_summary == "keeper" & exclude_trials == 1 ~ "5_not_enough_data",
      TRUE ~ exclude_summary
    )
  )



rm(data_eye_r, data_rezero)
```








## save eyetracking data for merged analysis
```{r}
data_clean %>%
  select(
    study, part_id, gender, order, trial_number, exclude_summary, exclude,
    age_in_months, age_group,
    lang_group, percent_english, percent_french, percent_other, child_ethnicity, years_education, lang_mix,
    phase, fam_type, trial_type,
    gaze_x, gaze_y, validity_left, validity_right, pupil_left, pupil_right, full_screen, track_loss, track_loss_reason, speaker_gender, movie_name, timestamp
  ) %>%
  mutate(trial_number = as.numeric(as.character(trial_number))) %>%
  saveRDS(here("output", "processed_data", "fp_preprocessed.Rdata"))
```
