---
title: "pupillometry analysis Study 2 (abbreviated as fp)"
output: html_document
---

# setup
## library() calls
see groundhog_packages.R for more package setup
```{r setup, include=FALSE}
# load all required libraries using the groundhog package (installs libraries that are not installed yet)
source("load_packages.R")


```


## define variables
```{r}
baseline_start <- 1800
baseline_end <- baseline_start + 200
analysis_start <- baseline_end
analysis_end <- 5000
bin_size <- 200
```


## read data
```{r pressure, echo=FALSE}
fp_data <- readRDS(here("output", "processed_data", "fp_preprocessed.Rdata"))
```


## save csv for reviewers to analyze without R
```{r}
fp_data %>% write_csv(here("output","processed_data", "csv_files", "pupil_all_data.csv"))
```

## remove non-keepers & keep only test phase
```{r}
fp_data <- fp_data %>%
  filter(exclude_summary == "keeper", phase == "test")
```
## number of participants
```{r}
fp_data %>%
  distinct(part_id, .keep_all = T) %>%
  group_by(age_group, lang_group) %>%
  count() %>%
  adorn_totals()
```


## create a unique trial variable
check if I need this
```{r}
fp_data <- fp_data %>%
  mutate(trial_unique = str_glue("{substr(study,1,1)}P_{part_id}_t{str_pad(trial_number,2,'left', '0')}"))
```



# preparation for pupillometry analysis
## check if there are trials where participant does not have pupil measures
```{r}
# identify any trials where the child has NO pupil data at all
has_pupil <- fp_data %>%
  mutate(mean_pupil = (pupil_left + pupil_right) / 2) %>%
  group_by(study, part_id, trial_number)

## during analysis window
has_pupil_analysis <- has_pupil %>%
  filter(between(
    timestamp,
    analysis_start,
    analysis_end + bin_size
  )) %>% # additional 100ms to get rid of extreme values at the end introduced by filtering and interpolation
  filter(any(!is.na(mean_pupil)))

## during baseline
has_pupil_baseline <- has_pupil %>%
  filter(between(timestamp, baseline_start, baseline_end)) %>%
  filter(any(!is.na(mean_pupil)))

# remove those trials from dataset, otherwise code will produce error
mtl_data_pupil <- fp_data %>%
  filter(trial_unique %in% has_pupil_analysis$trial_unique & trial_unique %in% has_pupil_baseline$trial_unique) %>%
  filter(between(timestamp, 1, analysis_end + bin_size))
```
## flag trials that have only trackloss and no data
if not done, regress_data does not work
```{r}
fp_data <- fp_data %>%
  mutate(mean_pupil = mean(c(pupil_left, pupil_right), na.rm = T)) %>%
  group_by(part_id, trial_number) %>%
  mutate(no_eye_data_for_full_trial = ifelse(all(is.na(mean_pupil) == TRUE), 1, 0)) %>%
  ungroup()
fp_data %>% tabyl(no_eye_data_for_full_trial)
```
## number of participants
```{r}
fp_data %>%
  distinct(part_id, .keep_all = T) %>%
  group_by(age_group, lang_group) %>%
  count() %>%
  adorn_totals()
```


## pupillometryR pre-processing 
### make_pupillometry_data
```{r}
# make pupilometry data
data_pupil <- make_pupillometryr_data(
  data = fp_data,
  subject = part_id,
  trial = trial_number,
  time = timestamp,
  condition = trial_type,
  other = lang_group
)
# plot(data_pupil, pupil = pupil_left, group = 'condition')
###
##
```
### regress missing values where only data from one eye is missing
```{r}
round(cor(data_pupil$pupil_left, data_pupil$pupil_right, use = "pairwise.complete.obs"), 2)
# correlation is very high, okay to regress

# regress data to smooth using data from one pupil to get the other
pupil_regress <-
  regress_data(
    data = data_pupil %>%
      filter(no_eye_data_for_full_trial != 1),
    pupil1 = pupil_left,
    pupil2 = pupil_right
  )
```


### average across pupils
```{r}
# get mean pupil sizes
averaged_pupil_size <- calculate_mean_pupil_size(
  data = pupil_regress,
  pupil1 = pupil_left,
  pupil2 = pupil_right
)

plot(averaged_pupil_size, pupil = mean_pupil, group = "condition")
```
### downsample to timebins
```{r}
# Calculating median pupil size in each timebin
downsampled_data <- downsample_time_data(
  data = averaged_pupil_size,
  pupil = mean_pupil,
  timebin_size = bin_size,
  option = "mean"
)

plot(downsampled_data, pupil = mean_pupil, group = "condition")
```


### look at missing data
```{r}

missing <- calculate_missing_data(
  downsampled_data,
  mean_pupil
)

removed_high_missing_data <- clean_missing_data(downsampled_data,
  pupil = mean_pupil,
  trial_threshold = .75,
  subject_trial_threshold = 1
)

# check how many trials we still have
dictionary_additional_part_to_exclude <- removed_high_missing_data %>%
  group_by(part_id, trial_type) %>%
  summarize(n_trials = n_distinct(trial_number)) %>%
  group_by(part_id) %>%
  mutate(trial_type = factor(trial_type)) %>%
  complete(trial_type, fill = list(n_trials = 0)) %>%
  pivot_wider(names_from = trial_type, values_from = n_trials) %>%
  mutate(exclude_not_enough_trials = ifelse(same == 0 | switch == 0, 1, 0)) %>%
  arrange(exclude_not_enough_trials)

# need to remove those that do not have 1 switch and 1 same trial
removed_high_missing_data <- removed_high_missing_data %>%
  full_join(dictionary_additional_part_to_exclude %>% select(part_id, exclude_not_enough_trials)) %>%
  filter(exclude_not_enough_trials == 0)


plot(removed_high_missing_data, pupil = mean_pupil, group = "condition")
```

#### number of participants before and after removing
```{r}
downsampled_data %>%
  separate(part_id, into = c("study", "id"), remove = F) %>%
  group_by(study, lang_group) %>%
  summarize(n = n_distinct(part_id)) %>%
  pivot_wider(names_from = lang_group, values_from = n) %>%
  adorn_totals()


removed_high_missing_data %>%
  separate(part_id, into = c("study", "id"), remove = F) %>%
  group_by(study, lang_group) %>%
  summarize(n = n_distinct(part_id)) %>%
  pivot_wider(names_from = study, values_from = n) %>%
  adorn_totals()
```
### trials before and after removing
```{r}
N_participants_before <- downsampled_data %>%
  summarize(participants = n_distinct(part_id)) %>%
  pull()

N_trials_before <- downsampled_data %>%
  distinct(part_id, trial_number) %>%
  count() %>%
  pull()


N_participants_after <- removed_high_missing_data %>%
  summarize(participants = n_distinct(part_id)) %>%
  pull()

N_trials_after <- removed_high_missing_data %>%
  distinct(part_id, trial_number) %>%
  count() %>%
  pull()

removed_by_pupillometry_r <- 65 # see output of clean_missing_data() above
removed_by_pupillometry_r / N_trials_before * 100
missingness_summary <- tibble(
  metric = c("participants", "trials"),
  before = c(N_participants_before, N_trials_before),
  after = c(N_participants_after, N_trials_after),
  removed = before - after,
  removed_percent = removed / before * 100
)
missingness_summary %>% write_csv(here("output", "tables", "pupil_Ns.csv"))
```


### filter data
```{r}
removed_high_missing_data %>%
  filter(timestamp < baseline_end) %>%
  mutate(na = is.na(mean_pupil)) %>%
  tabyl(Timebin, na)
# step to filter data
filtered_data <- filter_data(
  data = removed_high_missing_data,
  pupil = mean_pupil,
  filter = "median",
  degree = 11
) # package recommends 11, and it looks fine
filtered_data %>%
  filter(timestamp < baseline_end) %>%
  mutate(na = is.na(mean_pupil)) %>%
  tabyl(Timebin, na)
plot(filtered_data, pupil = mean_pupil, group = "condition")
```
### interpolate data 

```{r}
int_data <- interpolate_data(
  data = filtered_data,
  pupil = mean_pupil,
  type = "linear"
)
# Performing linear interpolation

plot(int_data, pupil = mean_pupil, group = "condition")
# removed the final timebin because the end got messed up with filtering/interpolation (very extreme values)
int_data %<>% filter(timestamp <= analysis_end)
```
## baseline
```{r}
base_data <- baseline_data(
  data = int_data,
  pupil = mean_pupil,
  start = baseline_start,
  stop = baseline_end
)

plot(base_data, pupil = mean_pupil, group = "condition") +
  geom_vline(xintercept = baseline_start) +
  geom_vline(xintercept = baseline_end)
```
# data analysis


## plot by study and age
```{r}
base_data %>%
  separate(part_id, c("study", "id"), sep = "_", remove = F) %>%
  filter(lang_group != "bilingual-other", between(timestamp, baseline_end - 300, analysis_end)) %>%
  mutate(time_from_onset = timestamp - 2000) %>%
  ggplot(., aes(x = time_from_onset, y = mean_pupil, colour = trial_type)) +
  geom_smooth(size = 1.5, fill = "lightgrey") +
  xlab("Time from onset of speech") +
  ylab("Change in pupil size") +
  facet_wrap(vars(study, lang_group), ncol = 4) +
  theme_classic() +
  theme(text = element_text(size = 20), legend.position = "bottom") +
  scale_color_brewer(palette = "Set2", name = "Trial Type")
ggsave(here("output", "figures", "pupil_dilation.png"), width = 15, height = 5)
```
## across whole time window
```{r}
whole_window <- base_data %>%
  subset_data(analysis_start, analysis_end) %>%
  create_window_data(
    data = .,
    pupil = mean_pupil
  )

plot(whole_window, pupil = mean_pupil, geom = "raincloud")
ggsave("pupil dilation.png")
```
## add in some variables that got lost in pipeline
```{r}
whole_window %<>%
  # add lang_group
  left_join(base_data %>% select(part_id, lang_group) %>% distinct()) %>%
  # get a separate study variable
  separate(part_id, into = c("study", "id"), sep = "_", remove = F) %>%
  mutate(
    age_group = str_extract(study, "\\d+"),
    study_type = substr(study, 1, 2),
    lang_group = relevel(factor(lang_group), ref = "monolingual")
  )



ggplot(whole_window, aes(x = trial_type, y = mean_pupil, group = part_id, colour = trial_type)) +
  geom_point() +
  geom_line(colour = "darkgrey") +
  facet_grid(rows = vars(age_group), cols = vars(lang_group))
```
## save csv for reviewers to analyze without R
```{r}
whole_window %>% write_csv(here("output","processed_data", "csv_files", "pupil_anova.csv"))
```

## number of participants
```{r}
whole_window %>%
  distinct(part_id, .keep_all = T) %>%
  group_by(age_group, lang_group) %>%
  count()
```

## anovas
```{r}
anova_FP_12mo <- whole_window %>%
  filter(age_group == "12") %>%
  ezANOVA(
    dv = mean_pupil,
    wid = part_id,
    within = trial_type,
    between = lang_group,
    return_aov = TRUE
  )
anova_FP_12mo
anova_FP_12mo_text <- convert_anova_to_apa_text(anova_FP_12mo)

anova_FP_18mo <- whole_window %>%
  filter(age_group == "18") %>%
  ezANOVA(
    dv = mean_pupil,
    wid = part_id,
    within = trial_type,
    between = lang_group,
    return_aov = TRUE
  )

(anova_FP_18mo_text <- convert_anova_to_apa_text(anova_FP_18mo))
```
# results
```{r}
results <- full_join(
  enframe(anova_FP_12mo_text, value = "anova_12mo_pupil") %>% unnest(cols = c(anova_12mo_pupil)),
  enframe(anova_FP_18mo_text, value = "anova_18mo_pupil") %>% unnest(cols = c(anova_18mo_pupil))
) %>%
  mutate(sort = nchar(name)) %>%
  arrange(sort, desc(name)) %>%
  select(-sort) %>%
  as_tibble()
results %>%
  write_csv(here("output", "tables", "fp_pupillometry.csv"))
```



## calculate mean change in pupil dilation
```{r}
summary <- whole_window %>%
  group_by(age_group, trial_type) %>%
  summarize(mean = round(mean(mean_pupil, na.rm = T), 3))

summary %>%
  write_csv(here("output", "tables", "fp_pupillometry_means.csv"))
```
