---
title: "LittlePrince Participant Background Info"
output:
  html_document:
    df_print: paged
---
# Script prep
## load packages

see groundhog_packages.R for more package setup
```{r setup, include=FALSE}
# load all required libraries using the groundhog package (installs libraries that are not installed yet)
source("load_packages.R")
```



# Read Participant Background info

```{r}

part_list <- readRDS(here("output", "processed_data", "anonymized_participant_info", "lp_part_info.Rdata"))
```






#  check exclusion criteria
## medical
### problems during pregnancy 

#### weeks at birth


```{r}
part_list %>%
  select(study, part_id, pregnancy) %>%
  filter(pregnancy > 42 |
    pregnancy < 37 |
    is.na(pregnancy)) %>%
  arrange(desc(pregnancy))

print("need to check, weeks at birth missing")
(missing.weeks <- part_list %>%
  filter(is.na(pregnancy)) %>%
  select(part_id, pregnancy))
# for LP5_P058, LP12_P073 and LP5_P014, we don't have the info (not in infant database, not in demographics)
# since premature birth is rare, will assume they were on term
# LP5_P026 is born at 37 weeks, corrected in demographics database
# LP12_P079 is actually 39 1/2 weeks, corrected to 40wks in filemaker demo quest
# LP12_P067 is actually 40 weeks (based on infant database)
print("outliers, check if correct")
(flagged.weeks <- part_list %>%
  filter(pregnancy > 43) %>%
  select(part_id, pregnancy))


part_list <- part_list %>% mutate(exclude_premature = ifelse(pregnancy < 37, 1, 0))
print("exclude for prematurity (based on gestation )")
(part_list %>% filter(exclude_premature == 1) %>% select(part_id, pregnancy))
```

#### birth weight


```{r}
part_list <- part_list %>% mutate(
  weightlbs = as.numeric(weightlbs),
  weight_oz_corrected = case_when(
    !is.na(weightlbs) & is.na(weightoz) ~ 0,
    weightoz > 16 ~ NA_real_,
    TRUE ~ as.numeric(weightoz)
  ),
  weight_lb_in_gram = weightlbs * 453 + weight_oz_corrected * 28.34,
  weight_in_grams_unified = ifelse(!is.na(weightgrams),
    weightgrams,
    weight_lb_in_gram
  )
)
```


#### now check which kids don't fit

used 2-5kg as reasonable weight at birth (anything lower or higher will be flagged as potentially unplausible. 97% for weight at birth is 4500 but we had a couple of babies between 4500 and 5000, and very few above 5000 so assume that is reasonable cutoff)
```{r}
(flagged.weight <- part_list %>%
  select(study, part_id, weight_in_grams_unified, weightgrams, weightlbs, weight_oz_corrected) %>%
  filter(!between(weight_in_grams_unified, 2000, 5000)) %>%
  arrange(desc(weightlbs)))

# LP12_P099, LP12_P051 no info on infant database
# LP12_P060 has 3269 at birth on infant database
# LP18_P016 is probably 8 pounds 9 oz instead of 91

missing.weight <- part_list %>%
  filter(is.na(weight_in_grams_unified)) %>%
  select(part_id, weight_in_grams_unified, weightgrams, weightlbs, weightoz)
# for LP12_P073,LP5_P035,LP5_P058  we don't have the info (not in infant database, not in demographics)
# for LP5_P064 database says term 37wks and birth weight 2720g > did not change on demo database but won't exclude that kid
```

#### exclude babies for prematurity (based on birth weight)
```{r}
part_list <- part_list %>% mutate(exclude_premature = case_when(
  weight_in_grams_unified < 2500 ~ 1,
  pregnancy < 37 ~ 1,
  weight_in_grams_unified >= 2500 ~ 0,
  pregnancy >= 37 ~ 0,
  TRUE ~ 0
)) # for babies with missing data, won't exclude them because prematurity is rare
print("exclude for prematurity (based on gestation and birth weight)")
(part_list %>% filter(exclude_premature == 1) %>% select(part_id, pregnancy, weight_in_grams_unified))
```
#### specific Pregnancy complications:

```{r}
part_list %>%
  select(part_id, complicationspregnancydetails, exclude_premature) %>%
  filter(!is.na(complicationspregnancydetails) & exclude_premature != 1)
```
I treat as serious: 
placenta abruption (LP12_P026)



### post-natal medical problems


#### General medical problems
```{r}
part_list %>%
  select(part_id, medicalproblemsdetails) %>%
  filter(!is.na(medicalproblemsdetails))
# seems ok
```
#### hearing-vision problems

```{r}
part_list %>%
  filter(
    !is.na(hearingvisionproblemsdetails),
    exclude_premature != 1
  ) %>%
  select(part_id, study, hearingvisionproblemsdetails)
# none excluded
```

#### current ear infection
- discussed with Krista and will not exclude for this, because parents aren't good at telling if a kid has an ear infection and it's not clear that Little prince would be very sensitive to excellent hearing vs ok hearing


```{r}
part_list %>%
  select(part_id, earinfectioncurrent) %>%
  filter(earinfectioncurrent %in% c("Oui", "Yes"))
table(part_list$earinfectioncurrent)
# after discussion wiht kbh, will not exclude these kids
```
#### current cold

```{r}

table(part_list$cold)
print("after discussion with KBH, did not exclude anyone because there's a lot of kids (parents have low thresholds?)")
```
#### other

```{r}
part_list %>%
  select(study, part_id, otherrelevantinfo) %>%
  filter(!is.na(otherrelevantinfo), !otherrelevantinfo %in% c("No", "Non", "no", "non", "NA"))
# exclude LP12_P095	born prematurely with underdeveloped lungs
# LP12_P095 is already excluded because born at 36 weeks.
```


### create summary variable exclude_medical
```{r}

part_list <- part_list %>%
  mutate(exclude_medical = case_when(
    exclude_premature == 1 ~ 0, # if already excluded for prematurity, no need to check medical conditions
    complicationspregnancydetails == "décollement du placenta" ~ 1,
    TRUE ~ 0
  ))
# which babies are excluded?
part_list %>%
  filter(exclude_medical == 1) %>%
  pull(part_id)
```

## check age criteria
using data from main subjects list (participant list)

### function to calculate age:
```{r}
average_days_per_month <- 365 / 12
# calculate ages
age_md <- function(x, scale = "months") {
  # takes an age in days and returns age in months and days
  months <- floor(x / average_days_per_month)
  days <- round(x - average_days_per_month * months)
  if (scale == "months") {
    return(months)
  } else if (scale == "days") {
    return(days)
  } else {
    stop("please enter either either months or days for argument scale")
  }
}
```
### create age range criteria
```{r}
age_ranges <- tibble(age_group = c(5, 12, 18), min_age_months = age_group - 1, max_age_months = age_group + 1)

# convert months to continuous age calculation
age_ranges <- age_ranges %>%
  mutate(
    min_age_continuous = min_age_months * average_days_per_month + 15,
    max_age_continuous = max_age_months * average_days_per_month + 15
  ) %>%
  # convert to time difference (adds days unit)
  mutate(
    min_age_continuous = as.difftime(min_age_continuous, units = "days"),
    max_age_continuous = as.difftime(max_age_continuous, units = "days")
  )

write_csv(age_ranges, here("data", "age_ranges.csv"))
```



### create age group variable

```{r}
part_list <- part_list %>%
  mutate(age_group = as.double(str_extract(study, "[0-9]{1,2}"))) %>%
  left_join(age_ranges %>% select(age_group, min_age_continuous, max_age_continuous), by = "age_group") # %>%

part_list <- part_list %>%
  rowwise() %>%
  mutate(exclude_age = case_when(
    between(as.numeric(age_in_days), as.numeric(min_age_continuous), as.numeric(max_age_continuous)) ~ 0,
    TRUE ~ 1
  )) %>%
  ungroup() %>%
  select(-min_age_continuous, -max_age_continuous)
```


 


## language criteria
### check language exposure

Check that % of langauge adds up to 100 +/- 1

```{r}
part_list$percent_total <- with(part_list, percent_english + percent_french + percent_other)
part_list %>%
  select(part_id, percent_total, percent_english, percent_french, percent_other) %>%
  filter(!(percent_total >= 99 & percent_total <= 101) | is.na(percent_total)) %>%
  arrange(desc(percent_total))
```


no more than 1% off from 100 - within margin of rounding error

### check language dominance assignment
```{r}

part_list <- part_list %>%
  rowwise() %>%
  mutate(
    dominant_language_old = dominant_language,
    dominant_language = str_to_title(dominant_language),
    dominant_en_fr = case_when(
      percent_english > percent_french ~ "English",
      percent_english < percent_french ~ "French",
      percent_english == percent_french ~ "Balanced"
    )
  )

# for this child, maternal language is English
part_list$dominant_en_fr[part_list$part_id == "LP12_P083"] <- "English"
# mom is bilingual (grew up hearing both English and French). Went with CDI -> more words in French
part_list$dominant_en_fr[part_list$part_id == "LP12_P027"] <- "French"

part_list %>%
  filter(dominant_en_fr == "Balanced") %>%
  select(part_id, study, percent_english, percent_french)
part_list %>%
  group_by(dominant_en_fr) %>%
  summarize(N = n())
# the only uncategorized balanced kids are non-keepers based on language
```




### flag kids for exclusion based on language exposure
 monolingual: at least 90% of either Eng or French 
 bilingual: at least 25 % exposure to French, 25% to English, no more than 10% to L3


```{r}
part_list <- part_list %>%
  mutate(
    lang_group = case_when(
      percent_english >= 90 | percent_french >= 90 ~ "monolingual",
      (percent_english >= 25 | percent_french >= 25) & percent_other >= 25 ~ "bilingual-other",
      percent_other > 20 ~ "none", # neither bilingual-other nor bilingual ( L3 criteria)
      between(percent_english, 25, 75) & between(percent_french, 25, 75) ~ "bilingual",
      TRUE ~ "none"
    ),
    lang_group = factor(lang_group)
  )

part_list %>% select(part_id, lang_group, percent_english, percent_french, percent_other)
```

### flag kids who don't fit either language group or are bilingual-other

```{r}

part_list <- part_list %>%
  mutate(exclude_language = ifelse(lang_group %in% c("none", "bilingual-other"), 1, 0))
```

## prior study exclusions
by accident, LP5_P012 participated again as LP12_P045 - keep only first visit
```{r}

# need to exclude the second visit at 12 months of age
part_list <- part_list %>%
  mutate(exclude_priorStudy = ifelse(part_id == "LP12_P045", 1, 0))
```
# final prep steps

## create Summary variable of reasons for exclusion

```{r}



part_list <- part_list %>% mutate(
  exclude_summary = case_when(
    exclude_priorStudy == 1 ~ "0_experimenterError", # should not have been scheduled
    age_group %in% c(9, 18) ~ "5_recruitment_stopped",
    exclude_age == 1 ~ "1_age", # should not have been scheduled
    exclude_premature == 1 ~ "2_preterm",
    exclude_medical == 1 ~ "3_health",
    lang_group == "bilingual-other" ~ "5_recruitment_stopped",
    exclude_language == 1 ~ "4_language",
    TRUE ~ "keeper"
  ),
  exclude = case_when(
    exclude_summary != "keeper" ~ 1,
    TRUE ~ 0
  )
)
```



## remove unnecessary variables
```{r}
part_list <- part_list %>%
  select(-exclude_age, -exclude_language, -exclude_premature, -exclude_priorStudy)
```





# Save file for next script

```{r}
export(part_list, file = here("output/processed_data/MainSubjList-lp4.Rdata"))
```
