
---
title: "LP04 merge eyetracking and participant info"
output:
  html_document:
    df_print: paged
---

######################
#####

# 1. Script prep 

## 1.1 install/load packages


## library() calls
see groundhog_packages.R for more package setup
```{r setup, include=FALSE}
# load all required libraries using the groundhog package (installs libraries that are not installed yet)
source("load_packages.R")
```


##  read in previously saved data

```{r}
# eyetracking data
eye_data_raw <- import(file = here("output", "processed_data", "fullData-lp2.Rdata"))

#####
# info on participants
part_list <- import(file = here("output", "processed_data", "MainSubjList-lp4.Rdata"))
```

## important columns for this script
```{r}
# from participant list
# define columns relevant for our study
info_for_analysis <- c(
  "part_id", "age_group", "lang_group", "gender", "dominant_language",
  "percent_english", "percent_french", "percent_other", "dominant_en_fr", "lang_mix",
  "study", "exclude", "exclude_summary", "age_in_months", "age_in_days", "years_education", "child_ethnicity"
)


# for future analysis
columns_to_keep <- c(
  "study", "part_id", "gender", "order",
  "trial_number", "exclude", "exclude_summary", "age_in_days",
  "age_in_months", "age_group", "lang_group", "percent_english",
  "percent_french", "percent_other", "child_ethnicity", "years_education", "lang_mix",
  "dominant_language", "dom_test", "phase", "trial_type", "gaze_x",
  "gaze_y", "validity_left", "validity_right", "pupil_left", "pupil_right",
  "full_screen", "speaker_gender", "movie_name", "timestamp", "test_pair",
  "track_loss", "track_loss_reason"
)
```


# Data frame cleaning
## check if any participants are not matching betwen master list and eyetracking data
ok can't use baby id to merge here, because we didn't use to enter babyid here
```{r}
print("missing from main subject list but present in eyetracking data")
(missing_from_part_list <- sort(setdiff(unique(eye_data_raw$part_id), part_list$part_id)))
stopifnot(missing_from_part_list == 0)

print("missing from eyetracking data but present in master subject list")

(missing_from_eyetracking <- sort(setdiff(part_list$part_id, eye_data_raw$part_id)))

# one of these is tested in condition we didn't pursue (LP18) and the other was experimenter error (file was lost)
```

## merge eyetracking data and participant info
```{r}
eye_full <- full_join(eye_data_raw,
  part_list %>%
    select(all_of(info_for_analysis)),
  by = c("study", "part_id")
)
```


## check if all participants are still in 
```{r}
eye_full %>%
  select(study, part_id) %>%
  distinct() %>%
  group_by(study) %>%
  summarize(N = n())
```

## create some necessary variables


### trial type, dominant language, phase,...       

```{r}
eye_full %<>% mutate(phase = factor(ifelse(trial_number <= 8,
  "familiarization",
  "test"
))) %>%
  separate(
    col = media_name,
    into = c("speaker_gender", "trial_language", "trial_type"),
    sep = "_",
    remove = FALSE
  ) %>%
  mutate(
    # actually, I prefer man/woman to male/female
    speaker_gender = case_when(
      speaker_gender == "Male" ~ "man",
      speaker_gender == "Fem" ~ "woman"
    ),
    media_name = as.character(media_name),
    familiarization_video_number = ifelse(phase == "familiarization", trial_type, as.character(NA)),
    trial_type = ifelse(phase == "test", tolower(trial_type), as.character(NA)),
    trial_language = case_when(
      trial_language == "Eng" ~ "English",
      trial_language == "Fr" ~ "French"
    ),
    trial_dominance = ifelse(dominant_en_fr == trial_language, "dominant", "non-dominant")
  ) %>%
  rename(movie_name = media_name)
```


### Switch into dominant or non-dominant language
maybe it's easier to tell if the switch is into the dominant language or into the non-dominant language. so need to know which gender the person where the switch is into the dominant language is (aka was speaking non-dom and in switch dom)
non-dominant language (aka was speaking dom and in switch now non-dominant)

```{r}
# order 1-4 have eng male and fr female
# 5-8 vice versa
eye_full %<>%
  group_by(part_id) %>%
  mutate(
    order_numeric = as.numeric(substr(order, 2, 2)),
    # which language are the woman and man speaking in fam
    man_fam = ifelse(order_numeric <= 4, "English", "French"),
    woman_fam = ifelse(order_numeric <= 4, "French", "English")
  ) %>%
  ungroup() %>%
  mutate( # who speaks the participants dominant language during familiarization?
    dom_fam = case_when(
      dominant_en_fr == man_fam ~ "man",
      dominant_en_fr == woman_fam ~ "woman"
    ),
    #    is the person who speaks dominant language in fam speaking? if yes, it is "switch into non-dominant" and vice versa

    # for test, only categorize test trials
    dom_test = case_when(
      phase == "familiarization" ~ as.character(NA),
      dom_fam == speaker_gender ~ "Switch into non-dominant language",
      dom_fam != speaker_gender ~ "Switch into dominant language"
    )
  )
```
### 1st test pair vs 2nd test pair
to see if attention decreases as test goes on
```{r}
eye_full %<>%
  mutate(test_pair = case_when(
    between(trial_number, 9, 10) ~ "pair1",
    between(trial_number, 11, 12) ~ "pair2",
    TRUE ~ as.character(NA)
  ))
```


# eyetracking preparation
### flag trials where there's track_loss/ looking outside of the screen

```{r}
eye_full %<>% mutate(
  track_loss_reason =
    case_when(
      between(validity_right, 2, 4) | between(validity_left, 2, 4) ~ "validity is bad", is.na(gaze_y) ~ "no info on coord y",
      is.na(gaze_x) ~ "no info on coord x",
      between(gaze_x, 0, 1920) ~ "",
      between(gaze_y, 0, 1200) ~ "",
      gaze_x < 0 | gaze_x > 1920 ~ "outside of box",
      gaze_y < 0 | gaze_y > 1200 ~ "outside of box",
      TRUE ~ "not sure"
    ),
  # create a logical tracklos variable for ease of use
  track_loss = ifelse(track_loss_reason != "", TRUE, FALSE)
)
```


### create AOI
for this study, it's the entire screen
```{r}
aoi_info <- data.frame(
  target_side = "full_screen",
  L = 0, R = 1920, # left, right
  `T` = 0, B = 1200 # top, bottom
)

# add aoi column using eyetrackingR
eye_full <- add_aoi(
  data = eye_full, aoi_dataframe = aoi_info,
  x_col = "gaze_x", y_col = "gaze_y",
  aoi_name = "full_screen"
)
```





## remove superfluous rows from eyetracker
without this, eyetrackingR complains when running eyetrackingR. Unfortunately, this code runs for about 20min!
```{r}
# clean up the workspace to hopefully speed up this process
rm(eye_data_raw)
gc()
# delete duplicated rows (artifact introduced by tobii eyetracker)
eye_full <- eye_full %>%
  select(all_of(columns_to_keep), studio_event) %>%
  arrange(part_id, timestamp, studio_event) %>%
  distinct(part_id, timestamp, .keep_all = T)
beepr::beep()
```

   
## convert data eyetrackingR format

```{r}
data <- make_eyetrackingr_data(eye_full,
  participant_column = "part_id",
  trial_column = "trial_number",
  time_column = "timestamp",
  trackloss_column = "track_loss",
  aoi_columns = "full_screen",
  treat_non_aoi_looks_as_missing = FALSE
) %>%
  mutate(trial_number = as.numeric(trial_number))
```
## rezero

this results in a warning on the 9 rows of participants who don't have any eyetracking data
```{r}
data <- data %>%
  mutate(time_from_start_of_study = timestamp)
# create a trial-specific timestamp (instead of timestamp relative to start of study)
data_rezero <- subset_by_window(data,
  window_start_msg = "MovieStart",
  window_end_msg = "MovieEnd",
  msg_col = "studio_event",
  rezero = T
)

# these are the participants the warning is for
data %>%
  group_by(part_id, movie_name, studio_event) %>%
  count() %>%
  spread(studio_event, n) %>%
  rename(all_other_rows = "<NA>") %>%
  arrange(all_other_rows)
```




## participant exclusion for not enough eyetracking data
### create df with unique trials by participant & samples per trial

```{r}
track_loss_info <- trackloss_analysis(data) %>%
  clean_names() %>%
  mutate(
    trial_number = as.numeric(trial_number),
    n_good_samples = samples - trackloss_samples
  ) %>%
  # get info on trial type
  # this is necessary because we need at least one trial of each test trial (same, switch)
  full_join(data %>%
    select(part_id, trial_number, trial_type, phase) %>%
    distinct(part_id, trial_number, .keep_all = TRUE))
```


 tracker collects data roughly every 17ms. so in 1s, should have 
1000/16.66667 = 60
 at least 60 samples


### check how many test trials with at least 60 samples I have

```{r}
summary_test_trials <- track_loss_info %>%
  group_by(part_id) %>%
  mutate(
    n_trials = max(trial_number) # ,
  ) %>%
  group_by(part_id, trial_type) %>%
  summarize(N = sum(n_good_samples >= 60)) %>%
  pivot_wider(names_from = trial_type, values_from = N) %>%
  mutate(
    exclude_data_quality = case_when(
      same >= 1 & switch >= 1 ~ 0,
      same == 0 | switch == 0 ~ 1,
      is.na(same) | is.na(switch) ~ 1,
      TRUE ~ as.numeric(NA)
    ),
    exclude_data_quality_summary = ifelse(
      exclude_data_quality == 1, "5_not_enough_data", "keeper"
    )
  )
```





# exclude participants with not enough trials
## merge in info about not enough trials



```{r}
data %<>%
  full_join(summary_test_trials %>% select(part_id, exclude_data_quality, exclude_data_quality_summary))

data <- data %>%
  mutate(
    exclude_data_quality = ifelse(is.na(exclude_data_quality), 1, exclude_data_quality),
    exclude_data_quality_summary = ifelse(is.na(exclude_data_quality_summary), "no ET data", exclude_data_quality_summary),
    exclude_summary = case_when(
      exclude_summary != "keeper" ~ exclude_summary,
      exclude_data_quality_summary != "keeper" ~ exclude_data_quality_summary,
      TRUE ~ exclude_summary
    ),
    exclude = case_when(
      exclude == 1 ~ 1,
      exclude == 0 & exclude_summary != "keeper" ~ 1,
      TRUE ~ exclude
    )
  )
```





# re-zero timestamp to start of trial
```{r}
# create a trial-specific timestamp (instead of timestamp relative to start of study)
data_rezero <- subset_by_window(data,
  window_start_msg = "MovieStart",
  window_end_msg = "MovieEnd",
  msg_col = "studio_event",
  rezero = T
)
```

# save data
```{r}
data_rezero %>%
  select(all_of(columns_to_keep)) %>%
  export(file = here("output", "processed_data", "fullData-lp5.Rdata"))
beepr::beep()
```
