---
title: "Eyetracking analysis script"


---

# script preparation
## library() calls
```{r setup, include=FALSE}
# devtools::install_github("psyteachr/introdataviz")
# devtools::install_github("rempsyc/rempsyc")

packages_used <- c(
  "rmarkdown", "codebook", "labelled", "devtools",
  "pander", "knitr", "forcats", "beepr",
  "anytime", "apaTables", "arsenal", "broom", "diffdf", "dplyr", "data.table",
  "eyetrackingR", "ez", "forcats", "ggbeeswarm", "ggplot2", "glue",
  "here", "janitor", "lme4", "lubridate", "magrittr",
  "Matrix", "purrr", "RColorBrewer",
  "readr", "readxl", "rio", "rlang", "stringr", "tibble",
  "tidyr", "tidylog", "TOSTER", "zoo"
)
for (i in packages_used) {
  library(i, character.only = T)
}
library(papaja)
library(introdataviz)
library(rempsyc)
```

# function
```{r}
# helper functions
# create function to get human readable non-latex code for results
convert_anova_to_apa_text <- function(input) {
  latex_result_table <- apa_print(input[["aov"]], in_paren = TRUE, es = "pes")
  latex_result_list <- latex_result_table$full_result
  latex_result_list %>%
    lapply(., function(x) gsub("\\$", "", x)) %>%
    lapply(., function(x) gsub("\\\\mathit\\{MSE\\}", "MSE", x)) %>%
    lapply(., function(x) gsub("\\\\hat\\{\\\\eta\\}\\^2_p", "eta2p", x))
}
```



## read littleprince data
```{r}
lp_data <- import(file = here("output", "processed_data", "fullData-lp5.Rdata"))
```


## read faceprince data
```{r pressure, echo=FALSE}
fp_data <- readRDS(here("output", "processed_data", "fp_preprocessed.Rdata")) %>%
  mutate(dominant_language = case_when(
    percent_english > percent_french ~ "English",
    percent_french > percent_english ~ "French",
    TRUE ~ "check"
  ))
```


## merge
```{r}
all_data <- full_join(fp_data, lp_data) %>%
  # shorten the study variable to study initials, keep the old study name as study_incl_age
  rename(study_incl_age = study) %>%
  mutate(
    study = glue("{substr(study_incl_age, 1,1)}P"),
    study = factor(study, levels = c("LP", "FP"))
  ) # want LP to always show first
```
## add variables
### direction of  switch variable
```{r}
all_data %<>%
  group_by(part_id) %>%
  mutate(
    order_numeric = as.numeric(substr(order, 2, 2)),
    # which language are the woman and man speaking in fam
    man_fam = ifelse(order_numeric <= 4, "English", "French"),
    woman_fam = ifelse(order_numeric <= 4, "French", "English")
  ) %>%
  ungroup() %>%
  mutate( # who speaks the participants dominant language during familiarization?
    dom_fam = case_when(
      dominant_language == man_fam ~ "man",
      dominant_language == woman_fam ~ "woman"
    ),
    #    is the person who speaks dominant language in fam speaking? if yes, it is "switch into non-dominant" and vice versa

    # for test, only categorize test trials
    dom_test = case_when(
      phase == "familiarization" ~ as.character(NA),
      dom_fam == speaker_gender ~ "Switch into non-dominant language",
      dom_fam != speaker_gender ~ "Switch into dominant language"
    )
  )
```
### create dominant language variable
```{r}
all_data %<>%
  mutate(
    percent_dominant = case_when(
      dominant_language == "English" ~ percent_english,
      dominant_language == "French" ~ percent_french
    ),
    percent_nondominant = case_when(
      dominant_language == "English" ~ percent_french,
      dominant_language == "French" ~ percent_english
    )
  )
```
## save csv for reviewers to analyze without R
```{r}
all_data %>% write_csv(here("output", "processed_data", "csv_files", "eyemovements_all_data.csv"))
```




# descriptive stuff
## excluded participants info
```{r}
#
all_data %>%
  distinct(part_id, .keep_all = TRUE) %>%
  group_by(study) %>%
  count(exclude_summary) %>%
  pivot_wider(names_from = study, values_from = n, values_fill = 0) %>%
  adorn_totals()
```
###  "not enough data" breakdown by age and language
```{r}
all_data %>%
  distinct(part_id, .keep_all = TRUE) %>%
  filter(exclude_summary == "5_not_enough_data") %>%
  group_by(study, age_group, lang_group) %>%
  count() %>%
  pivot_wider(values_from = n, names_from = lang_group)
```



### recruitment stopped category breakdown by age and language
```{r}
# breakdown of recruitment stopped group
all_data %>%
  distinct(part_id, .keep_all = TRUE) %>%
  filter(exclude_summary == "5_recruitment_stopped") %>%
  group_by(study, age_group, lang_group) %>%
  count()
```



## info about keepers
Table 1 in paper

xx could be made better by combining min max into a single range column
```{r}
table_1 <- all_data %>%
  filter(exclude_summary == "keeper") %>%
  distinct(interaction(part_id, study), .keep_all = T) %>%
  group_by(study, age_group, lang_group) %>%
  summarize(
    N = n(),
    min = round(min(age_in_months, na.rm = T), 1),
    mean = round(mean(age_in_months, na.rm = T), 1),
    max = round(max(age_in_months, na.rm = T), 1),
    mean_gender = as.integer(round(mean(gender == "female", na.rm = T) * 100, 0)),
    mean_eng = as.integer(round(mean(dominant_language == "English") * 100, 0)) # this assumes there is no NA!
  ) %>%
  ungroup()

table_1 %>%
  write_csv(here("output", "tables", "table1.csv"))
```

## language exposure
```{r}
desc_language <- all_data %>%
  filter(exclude_summary == "keeper") %>%
  distinct(interaction(part_id, study), .keep_all = T) %>%
  group_by(study, lang_group) %>%
  summarise_at(vars(percent_dominant, percent_nondominant),
    list(mean = mean, min = min, max = max),
    na.rm = T
  ) %>%
  mutate(across(ends_with("mean"), round)) %>%
  relocate(contains("nondominant"), .after = percent_dominant_max)
```

## exposure to third language and language mixing scores(bilinguals only)
```{r}
all_data %>%
  filter(exclude_summary == "keeper", lang_group == "bilingual", percent_other > 0) %>%
  distinct(part_id, .keep_all = T) %>%
  group_by(study, .drop = F) %>%
  summarize(
    n = n(),
    min = min(percent_other),
    max = max(percent_other),
    mean = mean(percent_other)
  )



all_data %>%
  filter(exclude_summary == "keeper", lang_group == "bilingual") %>%
  distinct(part_id, .keep_all = T) %>%
  group_by(study, .drop = F) %>%
  summarize(
    mean_mixing = mean(lang_mix, na.rm = T),
    range = range(lang_mix, na.rm = T),
    n_missing = sum(is.na(lang_mix))
  )
```



## ethnicity and maternal education
```{r}
# ethnicity LP
all_data %>%
  filter(exclude_summary == "keeper", study == "LP") %>%
  distinct(part_id, .keep_all = T) %>%
  tabyl(child_ethnicity) %>%
  mutate(percent = round(percent, 2) * 100) %>%
  arrange(-n)
# ethnicity FP
all_data %>%
  filter(exclude_summary == "keeper", study == "FP") %>%
  distinct(part_id, .keep_all = T) %>%
  tabyl(child_ethnicity) %>%
  mutate(percent = round(percent, 2) * 100) %>%
  arrange(-n)

# education
all_data %>%
  filter(exclude_summary == "keeper") %>%
  distinct(part_id, .keep_all = T) %>%
  group_by(study) %>%
  summarize(mean = round(mean(years_education, na.rm = T), 1))
```

## average number of trials
```{r}
all_data %>%
  filter(exclude_summary == "keeper", exclude != 1) %>%
  group_by(study, age_group, part_id) %>%
  summarize(N_trials = mean(n_distinct(trial_number))) %>%
  group_by(study, age_group) %>%
  summarize(mean_trials = round(mean(N_trials), 1))
```

## change in looking to familiarization over trials
```{r}
keeper_data_all_trials <- all_data %>%
  filter(exclude_summary == "keeper") %>%
  make_eyetrackingr_data(
    participant_column = "part_id",
    trial_column = "trial_number",
    time_column = "timestamp",
    trackloss_column = "track_loss",
    aoi_columns = c("full_screen"),
    treat_non_aoi_looks_as_missing = FALSE
  )


response_window_agg_by_sub_all_trials <- make_time_window_data(keeper_data_all_trials,
  aois = "full_screen",
  predictor_columns = c("study", "lang_group", "age_group", "trial_type", "trial_number", "percent_dominant", "lang_mix"),
  summarize_by = "part_id"
) %>%
  group_by(part_id, study, lang_group, age_group, percent_dominant, lang_mix, trial_type, trial_number) %>%
  summarize(mean_LT = mean(SamplesInAOI / 60, na.rm = T))


trial_change_summary <- response_window_agg_by_sub_all_trials %>%
  mutate(trial_number = as.numeric(trial_number)) %>%
  group_by(study, trial_number) %>%
  summarize(
    mean = round(mean(mean_LT, na.rm = T), 1),
    sd = round(sd(mean_LT, na.rm = T), 1)
  )


trial_change_summary %>%
  pivot_wider(names_from = study, values_from = c(mean, sd)) %>%
  relocate(sd_LP, .after = mean_LP) %>%
  rename(
    Study1_mean = mean_LP,
    Study1_SD = sd_LP,
    Study2_mean = mean_FP,
    Study2_SD = sd_FP
  ) %>%
  View()

t_test_data <- response_window_agg_by_sub_all_trials %>%
  filter(as.numeric(trial_number) < 9) %>%
  group_by(part_id) %>%
  slice(c(1, n())) %>%
  mutate(fam_trial = factor(case_when(
    trial_number %in% c(1, 2) ~ "first",
    trial_number %in% c(6, 7, 8) ~ "last"
  )))

# calculate cohen's d
t_test_data %>%
  group_by(study, fam_trial) %>%
  summarize(
    mean = round(mean(mean_LT, na.rm = T), 1),
    sd = round(sd(mean_LT, na.rm = T), 1)
  ) %>%
  pivot_wider(names_from = fam_trial, values_from = c(mean, sd)) %>%
  group_by(study) %>%
  mutate(cohen_d = round((mean_first - mean_last) / ((sd_first + sd_last) / 2), 2))

# little prince (study 1) t-test
t_test_data %>%
  filter(study == "LP") %>%
  t.test(mean_LT ~ fam_trial, data = ., paired = T, idvar = "part_id")

# faceprince (study 2) t-test
t_test_data %>%
  filter(study == "FP") %>%
  t.test(mean_LT ~ fam_trial, data = ., paired = T, idvar = "part_id")
```
```




# prep eyetracking analysis
```{r}
keeper_data <- all_data %>%
  filter(exclude_summary == "keeper") %>%
  filter(phase == "test") %>%
  make_eyetrackingr_data(
    participant_column = "part_id",
    trial_column = "trial_number",
    time_column = "timestamp",
    trackloss_column = "track_loss",
    aoi_columns = c("full_screen"),
    treat_non_aoi_looks_as_missing = FALSE
  )


response_window_agg_by_sub <- make_time_window_data(keeper_data,
  aois = "full_screen",
  predictor_columns = c("study", "lang_group", "age_group", "trial_type", "trial_number", "percent_dominant", "lang_mix"),
  summarize_by = "part_id"
) %>%
  group_by(part_id, study, lang_group, age_group, percent_dominant, lang_mix, trial_type) %>%
  summarize(mean_LT = mean(SamplesInAOI / 60, na.rm = T))


response_window_agg_by_sub %>%
  distinct(part_id, .keep_all = TRUE) %>%
  group_by(study, age_group, lang_group) %>%
  count() %>%
  pivot_wider(names_from = lang_group, values_from = n) %>%
  arrange(desc(study))
```

## wide df with differential looking time 
```{r}
response_window_wide <- response_window_agg_by_sub %>%
  select(part_id, study, lang_group, age_group, trial_type, percent_dominant, mean_LT) %>%
  pivot_wider(names_from = trial_type, values_from = mean_LT) %>%
  mutate(diff_LT = switch - same)
```



## log transformation
```{r}
# take a quick peek at data
response_window_agg_by_sub %>% ggplot(., aes(x = study, y = mean_LT)) +
  geom_violin()

response_window_agg_by_sub %<>%
  mutate(mean_LT_log = log(mean_LT))


# log-transformed data
response_window_agg_by_sub %>% ggplot(., aes(x = study, y = mean_LT_log)) +
  geom_violin()
```



## calculate mean looking times & effect sizes
```{r}
table_1 <- response_window_agg_by_sub %>%
  group_by(study, age_group, lang_group, trial_type) %>%
  summarize(
    mean = mean(mean_LT),
    SD = sd(mean_LT)
  ) %>%
  pivot_wider(values_from = c(mean, SD), names_from = trial_type) %>%
  mutate(cohen_d = (mean_switch - mean_same) / ((SD_same + SD_switch) / 2)) %>%
  mutate(across(mean_same:cohen_d, round, 2)) %>%
  relocate(SD_same, .before = mean_switch)

table_1 %>%
  mutate(
    age_group = case_when(
      age_group == 5 ~ "5-month-olds",
      age_group == 12 ~ "12-month-olds",
      age_group == 18 ~ "18-month-olds"
    ),
    lang_group = case_when(
      lang_group == "bilingual" ~ "Bilinguals",
      lang_group == "monolingual" ~ "Monolinguals"
    ),
    study = case_when(
      study == "LP" ~ "Study 1",
      study == "FP" ~ "Study 2"
    )
  ) %>%
  nice_table() %>%
  save_as_docx(., path = here("output", "tables", "means_table.docx"))
```



### looking times for biling vs monoling
```{r}
# bilinguals vs monolinguals
response_window_agg_by_sub %>%
  group_by(study, age_group, lang_group) %>%
  summarize(
    mean = mean(mean_LT),
    SD = sd(mean_LT)
  ) %>%
  pivot_wider(values_from = c(mean, SD), names_from = lang_group) %>%
  mutate(cohen_d = (mean_bilingual - mean_monolingual) / ((SD_bilingual + SD_monolingual) / 2)) %>%
  mutate(across(mean_bilingual:cohen_d, round, 2)) %>%
  select(-starts_with("SD"))
```


### total looking time across trial types

```{r}
response_window_agg_by_sub %>%
  group_by(study, age_group) %>%
  summarize(mean_LT = round(mean(mean_LT), 2))
```


# Main analyses



## nhst looking times


### save csv for reviewers to analyze without R
```{r}
response_window_agg_by_sub %>% write_csv(here("output", "processed_data", "csv_files", "eyemovements_anova.csv"))
```

### descriptive tables of measn
```{r}
```


### run anova on logtransformed data
```{r}
anova_LP_5mo <- response_window_agg_by_sub %>%
  filter(age_group == 5, study == "LP") %>%
  ezANOVA(
    dv = mean_LT_log,
    wid = part_id,
    within = trial_type,
    between = lang_group,
    return_aov = TRUE
  )
anova_LP_12mo <- response_window_agg_by_sub %>%
  filter(age_group == 12, study == "LP") %>%
  ezANOVA(
    dv = mean_LT_log,
    wid = part_id,
    within = trial_type,
    between = lang_group,
    return_aov = TRUE
  )
anova_FP_12mo <- response_window_agg_by_sub %>%
  filter(age_group == 12, study == "FP") %>%
  ezANOVA(
    dv = mean_LT_log,
    wid = part_id,
    within = trial_type,
    between = lang_group,
    return_aov = TRUE
  )

anova_FP_18mo <- response_window_agg_by_sub %>%
  filter(age_group == 18, study == "FP") %>%
  ezANOVA(
    dv = mean_LT_log,
    wid = part_id,
    within = trial_type,
    between = lang_group,
    return_aov = TRUE
  )



# convert to suitable in-text output
anova_LP_5mo_text <- convert_anova_to_apa_text(anova_LP_5mo)
anova_LP_12mo_text <- convert_anova_to_apa_text(anova_LP_12mo)
anova_FP_12mo_text <- convert_anova_to_apa_text(anova_FP_12mo)
anova_FP_18mo_text <- convert_anova_to_apa_text(anova_FP_18mo)
```
### robustness analysis: anova
done on untransformed looking times to see if same pattern of results holds up
```{r}
anova_LP_5mo_robust <- response_window_agg_by_sub %>%
  filter(age_group == 5, study == "LP") %>%
  ezANOVA(
    dv = mean_LT,
    wid = part_id,
    within = trial_type,
    between = lang_group,
    return_aov = TRUE
  )
anova_LP_12mo_robust <- response_window_agg_by_sub %>%
  filter(age_group == 12, study == "LP") %>%
  ezANOVA(
    dv = mean_LT,
    wid = part_id,
    within = trial_type,
    between = lang_group,
    return_aov = TRUE
  )
anova_FP_12mo_robust <- response_window_agg_by_sub %>%
  filter(age_group == 12, study == "FP") %>%
  ezANOVA(
    dv = mean_LT,
    wid = part_id,
    within = trial_type,
    between = lang_group,
    return_aov = TRUE
  )

anova_FP_18mo_robust <- response_window_agg_by_sub %>%
  filter(age_group == 18, study == "FP") %>%
  ezANOVA(
    dv = mean_LT,
    wid = part_id,
    within = trial_type,
    between = lang_group,
    return_aov = TRUE
  )



# convert to suitable in-text output
anova_LP_5mo_text_robust <- convert_anova_to_apa_text(anova_LP_5mo_robust)
anova_LP_12mo_text_robust <- convert_anova_to_apa_text(anova_LP_12mo_robust)
anova_FP_12mo_text_robust <- convert_anova_to_apa_text(anova_FP_12mo_robust)
anova_FP_18mo_text_robust <- convert_anova_to_apa_text(anova_FP_18mo_robust)
```
### results of log-transformed and untransformed ANOVAs
```{r}
aov_LP_05mo <- full_join(
  enframe(anova_LP_5mo_text, value = "text") %>% unnest(cols = c(text)),
  enframe(anova_LP_5mo_text_robust, value = "robust") %>% unnest(cols = c(robust))
) %>%
  mutate(sort = nchar(name), group = "lp5mo") %>%
  arrange(sort, desc(name))

aov_LP_12mo <- full_join(
  enframe(anova_LP_12mo_text, value = "text") %>% unnest(cols = c(text)),
  enframe(anova_LP_12mo_text_robust, value = "robust") %>% unnest(cols = c(robust))
) %>%
  mutate(sort = nchar(name), group = "lp12mo") %>%
  arrange(sort, desc(name))

aov_FP_12mo <- full_join(
  enframe(anova_FP_12mo_text, value = "text") %>% unnest(cols = c(text)),
  enframe(anova_FP_12mo_text_robust, value = "robust") %>% unnest(cols = c(robust))
) %>%
  mutate(sort = nchar(name), group = "fp12mo") %>%
  arrange(sort, desc(name))

aov_FP_18mo <- full_join(
  enframe(anova_FP_18mo_text, value = "text") %>% unnest(cols = c(text)),
  enframe(anova_FP_18mo_text_robust, value = "robust") %>% unnest(cols = c(robust))
) %>%
  mutate(sort = nchar(name), group = "fp18mo") %>%
  arrange(sort, desc(name))

all <- rbind(aov_LP_05mo, aov_LP_12mo, aov_FP_12mo, aov_FP_18mo) %>% as_tibble()

all %>% write_csv(here("output", "tables", "looking_time_nhst_results.csv"))
```



## equivalence tests
```{r}
# smallest effect size of interest
expected_min_effect_size <- 0.5118
verbose_var <- FALSE

# convert response df to wide to make calculation easier
response_window_wide_log <- response_window_agg_by_sub %>%
  select(part_id, study, lang_group, lang_mix, age_group, trial_type, percent_dominant, mean_LT_log) %>%
  pivot_wider(names_from = trial_type, values_from = mean_LT_log)

# this preps the data for use with purr::map and tost
# summarize by study and age group
tost_df_study <- response_window_wide_log %>%
  group_by(study, age_group) %>%
  summarize(
    N = n(),
    mean.1 = mean(same),
    mean.2 = mean(switch),
    sd.1 = sd(same),
    sd.2 = sd(switch),
    corr = cor(same, switch)
  ) %>%
  ungroup()


TOST_results <- tost_df_study %>%
  # separate the data by Study and language background
  nest(-study, -age_group) %>%
  # compute equivalence test
  mutate(results_of_equ_test = purrr::map(
    data,
    ~ TOSTpaired(
      n = .$N,
      m1 = .$mean.1,
      m2 = .$mean.2,
      sd1 = .$sd.1,
      sd2 = .$sd.2,
      r12 = .$corr,
      high_eqbound = expected_min_effect_size,
      low_eqbound = -expected_min_effect_size,
      verbose = verbose_var
    )
  )) %>%
  # convert results to tibble
  mutate(tidied = purrr::map(results_of_equ_test, as_tibble)) %>%
  # make results easier to view
  unnest(tidied, .drop = TRUE) %>%
  group_by(study, age_group) %>%
  mutate(
    max_t = ifelse(abs(TOST_t1) < abs(TOST_t2), TOST_t1, TOST_t2),
    max_p = max(TOST_p1, TOST_p2),
    full_result = ifelse(round(max_t, 2) == 0,
      sprintf("t[%d] = %.2f, p = %.3f", TOST_df, max_t, max_p),
      sprintf("t[%d] = %.2f, p = %.3f", TOST_df, max_t, max_p) # same result for if and else?
    )
  ) %>%
  ungroup()
```

### robustness analysis: untransformed equivalence tests
```{r}
# this preps the data for use with purr::map and tost
# summarize by study and age group
tost_df_study_untransformed <- response_window_wide %>%
  group_by(study, age_group) %>%
  summarize(
    N = n(),
    mean.1 = mean(same),
    mean.2 = mean(switch),
    sd.1 = sd(same),
    sd.2 = sd(switch),
    corr = cor(same, switch)
  ) %>%
  ungroup()


TOST_results_untransformed <- tost_df_study_untransformed %>%
  # separate the data by Study and language background
  nest(-study, -age_group) %>%
  # compute equivalence test
  mutate(results_of_equ_test = purrr::map(
    data,
    ~ TOSTpaired(
      n = .$N,
      m1 = .$mean.1,
      m2 = .$mean.2,
      sd1 = .$sd.1,
      sd2 = .$sd.2,
      r12 = .$corr,
      high_eqbound = expected_min_effect_size,
      low_eqbound = -expected_min_effect_size,
      verbose = verbose_var
    )
  )) %>%
  # convert results to tibble
  mutate(tidied = purrr::map(results_of_equ_test, as_tibble)) %>%
  # make results easier to view
  unnest(tidied, .drop = TRUE) %>%
  group_by(study, age_group) %>%
  mutate(
    max_t = ifelse(abs(TOST_t1) < abs(TOST_t2), TOST_t1, TOST_t2),
    max_p = max(TOST_p1, TOST_p2),
    full_result = ifelse(round(max_t, 2) == 0,
      sprintf("t[%d] = %.2f, p = %.3f", TOST_df, max_t, max_p),
      sprintf("t[%d] = %.2f, p = %.3f", TOST_df, max_t, max_p) # No difference between if/else result
    )
  ) %>%
  ungroup()
```




### visualizations
```{r}
# plot with images to better understand tests

tost_df_study %>%
  slice(1) %>%
  glue_data("Study {study} - {age_group}-month-olds")
with(
  tost_df_study %>% slice(1),
  TOSTpaired(
    n = N, m1 = mean.1, m2 = mean.2, sd1 = sd.1, sd2 = sd.2,
    r12 = corr,
    high_eqbound_dz = expected_min_effect_size,
    low_eqbound_dz = -expected_min_effect_size,
    verbose = verbose_var
  )
)
tost_df_study %>%
  slice(2) %>%
  glue_data("Study {study} - {age_group}-month-olds")
with(
  tost_df_study %>% slice(2),
  TOSTpaired(
    n = N, m1 = mean.1, m2 = mean.2, sd1 = sd.1, sd2 = sd.2,
    r12 = corr,
    high_eqbound_dz = expected_min_effect_size,
    low_eqbound_dz = -expected_min_effect_size,
    verbose = verbose_var
  )
)
tost_df_study %>%
  slice(3) %>%
  glue_data("Study {study} - {age_group}-month-olds")
with(
  tost_df_study %>% slice(3),
  TOSTpaired(
    n = N, m1 = mean.1, m2 = mean.2, sd1 = sd.1, sd2 = sd.2,
    r12 = corr,
    high_eqbound_dz = expected_min_effect_size,
    low_eqbound_dz = -expected_min_effect_size,
    verbose = verbose_var
  )
)
tost_df_study %>%
  slice(4) %>%
  glue_data("Study {study} - {age_group}-month-olds")
with(
  tost_df_study %>% slice(4),
  TOSTpaired(
    n = N, m1 = mean.1, m2 = mean.2, sd1 = sd.1, sd2 = sd.2,
    r12 = corr,
    high_eqbound_dz = expected_min_effect_size,
    low_eqbound_dz = -expected_min_effect_size,
    verbose = verbose_var
  )
)
```
### comparison
```{r}
eq_tests <- tibble(TOST_results$study, TOST_results$age_group,
  log_transformed = TOST_results$full_result,
  untransformed = TOST_results_untransformed$full_result
) %>% rename(study = `TOST_results$study`, age_group = `TOST_results$age_group`)
eq_tests
```


## PLOT split violin plot

```{r}
ggplot(
  response_window_wide,
  aes(
    x = factor(age_group),
    y = diff_LT,
    fill = lang_group
  )
) +
  geom_hline(aes(yintercept = 0), colour = "darkgrey") +
  introdataviz::geom_split_violin(alpha = .4, trim = FALSE) +
  geom_boxplot(width = .2, alpha = .6, fatten = NULL, show.legend = FALSE) +
  stat_summary(
    fun.data = "mean_se", geom = "pointrange", show.legend = F,
    position = position_dodge(.175)
  ) +
  facet_wrap(vars(study),
    scales = "free_x",
    labeller = labeller(study = c(
      "LP" = "Auditory-Only",
      "FP" = "Audiovisual"
    ))
  ) +
  scale_x_discrete(name = "Age Group (in months)") +
  scale_y_continuous(name = "Difference in s (Switch-Same)") +
  scale_fill_brewer(palette = "Set1", name = "Language Group") +
  theme_apa() +
  theme(text = element_text(size = 20), legend.position = "right")
ggsave(here("output", "figures", "LPFP_paper.png"), width = 12, height = 6)
```


# exploratory analysis
## correlation between diff LT and % dominant
### log-transformed looking time
```{r}
response_window_wide_log %<>%
  mutate(diff_LT = switch - same)

# LP 5-month-olds
cor_LP_5_lang_dom <- with(
  response_window_wide_log %>%
    filter(study == "LP", age_group == 5),
  cor.test(
    diff_LT,
    percent_dominant
  )
) %>%
  apa_print(in_paren = TRUE)

# LP 12-month-olds
cor_LP_12_lang_dom <- with(
  response_window_wide_log %>%
    filter(study == "LP", age_group == 12),
  cor.test(
    diff_LT,
    percent_dominant
  )
) %>%
  apa_print(in_paren = TRUE)

# FP 12-month-olds
cor_FP_12_lang_dom <- with(
  response_window_wide_log %>%
    filter(study == "FP", age_group == 12),
  cor.test(
    diff_LT,
    percent_dominant
  )
) %>%
  apa_print(in_paren = TRUE)

# FP 18-month-olds
cor_FP_18_lang_dom <- with(
  response_window_wide_log %>%
    filter(study == "FP", age_group == 18),
  cor.test(
    diff_LT,
    percent_dominant
  )
) %>%
  apa_print(in_paren = TRUE)
ggplot(response_window_wide, aes(percent_dominant, diff_LT, colour = factor(age_group))) +
  geom_smooth(method = "lm") +
  geom_point() +
  facet_grid(cols = vars(study))
# corr_lang_dom  =  tibble(study= c(1,2), report_latex = c(cor_study_1_lang_dom$full_result, cor_study_2_lang_dom$full_result)) %>%
# get rid of latex formatting
#  mutate(report_word = convert_anova_to_apa_text(report_latex))
```

### robustness analysis: untransformed LT
```{r}
# LP 5-month-olds
cor_LP_5_lang_dom_untransformed <- with(
  response_window_wide %>%
    filter(study == "LP", age_group == 5),
  cor.test(
    diff_LT,
    percent_dominant
  )
) %>%
  apa_print(in_paren = TRUE)

# LP 12-month-olds
cor_LP_12_lang_dom_untransformed <- with(
  response_window_wide %>%
    filter(study == "LP", age_group == 12),
  cor.test(
    diff_LT,
    percent_dominant
  )
) %>%
  apa_print(in_paren = TRUE)

# FP 12-month-olds
cor_FP_12_lang_dom_untransformed <- with(
  response_window_wide %>%
    filter(study == "FP", age_group == 12),
  cor.test(
    diff_LT,
    percent_dominant
  )
) %>%
  apa_print(in_paren = TRUE)

# FP 18-month-olds
cor_FP_18_lang_dom_untransformed <- with(
  response_window_wide %>%
    filter(study == "FP", age_group == 18),
  cor.test(
    diff_LT,
    percent_dominant
  )
) %>%
  apa_print(in_paren = TRUE)
```
### results
pattern of results the same with and without logtransformation
```{r}
correlation_dominant_language <- tibble(
  analysis = c("log_transformed", "untransformed"),
  lp_5mo = c(
    cor_LP_5_lang_dom$full_result,
    cor_LP_5_lang_dom_untransformed$full_result
  ),
  lp_12mo = c(
    cor_LP_12_lang_dom$full_result,
    cor_LP_12_lang_dom_untransformed$full_result
  ),
  fp_12mo = c(
    cor_FP_12_lang_dom$full_result,
    cor_FP_12_lang_dom_untransformed$full_result
  ),
  fp_18mo = c(
    cor_FP_18_lang_dom$full_result,
    cor_FP_18_lang_dom_untransformed$full_result
  )
)
correlation_dominant_language %<>% pivot_longer(!analysis, names_to = "analysis_type", values_to = "result") %>% pivot_wider(names_from = analysis, values_from = result)
correlation_dominant_language <- correlation_dominant_language %>%
  mutate(log_transformed = gsub("\\$|\\\\", "", log_transformed)) %>%
  mutate(untransformed = gsub("\\$|\\\\", "", untransformed))
```
## correlation with language mixing scale
### log-transformed
```{r}
response_window_wide_log %>%
  filter(lang_group == "bilingual") %>%
  group_by(study, age_group) %>%
  summarize(n_distinct(part_id))
# LP 5-month-olds
cor_LP_5_lang_mix <- with(
  response_window_wide_log %>%
    filter(study == "LP", age_group == 5, lang_group == "bilingual"),
  cor.test(
    diff_LT,
    lang_mix
  )
) %>%
  apa_print(in_paren = TRUE)

# LP 12-month-olds
cor_LP_12_lang_mix <- with(
  response_window_wide_log %>%
    filter(study == "LP", age_group == 12, lang_group == "bilingual"),
  cor.test(
    diff_LT,
    lang_mix
  )
) %>%
  apa_print(in_paren = TRUE)

# FP 12-month-olds
cor_FP_12_lang_mix <- with(
  response_window_wide_log %>%
    filter(study == "FP", age_group == 12, lang_group == "bilingual"),
  cor.test(
    diff_LT,
    lang_mix
  )
) %>%
  apa_print(in_paren = TRUE)

# FP 18-month-olds
cor_FP_18_lang_mix <- with(
  response_window_wide_log %>%
    filter(study == "FP", age_group == 18, lang_group == "bilingual"),
  cor.test(
    diff_LT,
    lang_mix
  )
) %>%
  apa_print(in_paren = TRUE)
ggplot(response_window_wide, aes(lang_mix, diff_LT, colour = factor(age_group))) +
  geom_smooth(method = "lm") +
  geom_point() +
  facet_grid(cols = vars(study))
```

### robustness: untransformed
```{r}
# LP 5-month-olds
cor_LP_5_lang_mix_untrans <- with(
  response_window_wide %>%
    filter(study == "LP", age_group == 5, lang_group == "bilingual"),
  cor.test(
    diff_LT,
    lang_mix
  )
) %>%
  apa_print(in_paren = TRUE)

# LP 12-month-olds
cor_LP_12_lang_mix_untrans <- with(
  response_window_wide %>%
    filter(study == "LP", age_group == 12, lang_group == "bilingual"),
  cor.test(
    diff_LT,
    lang_mix
  )
) %>%
  apa_print(in_paren = TRUE)

# FP 12-month-olds
cor_FP_12_lang_mix_untrans <- with(
  response_window_wide %>%
    filter(study == "FP", age_group == 12, lang_group == "bilingual"),
  cor.test(
    diff_LT,
    lang_mix
  )
) %>%
  apa_print(in_paren = TRUE)

# FP 18-month-olds
cor_FP_18_lang_mix_untrans <- with(
  response_window_wide %>%
    filter(study == "FP", age_group == 18, lang_group == "bilingual"),
  cor.test(
    diff_LT,
    lang_mix
  )
) %>%
  apa_print(in_paren = TRUE)
```

### comparison
pattern of results the same with and without logtransformation
```{r}
correlation_lang_mix <- tibble(
  analysis = c("log_transformed", "untransformed"),
  lp_5mo = c(
    cor_LP_5_lang_mix$full_result,
    cor_LP_5_lang_mix_untrans$full_result
  ),
  lp_12mo = c(
    cor_LP_12_lang_mix$full_result,
    cor_LP_12_lang_mix_untrans$full_result
  ),
  fp_12mo = c(
    cor_FP_12_lang_mix$full_result,
    cor_FP_12_lang_mix_untrans$full_result
  ),
  fp_18mo = c(
    cor_FP_18_lang_mix$full_result,
    cor_FP_18_lang_mix_untrans$full_result
  )
)
correlation_lang_mix %<>%
  pivot_longer(!analysis, names_to = "analysis_type", values_to = "result") %>% pivot_wider(names_from = analysis, values_from = result)
correlation_lang_mix <- correlation_lang_mix %>%
  mutate(log_transformed = gsub("\\$|\\\\", "", log_transformed)) %>%
  mutate(untransformed = gsub("\\$|\\\\", "", untransformed))
```

## difference by direction of switch
### prep data
get difference in looking time for same and switch trial separately for the speaker who switched into dominant language and out of dominant language. then do an anova with only those who have all four test trials. 
```{r}
response_window_agg_by_sub_dominance <- make_time_window_data(keeper_data,
  aois = "full_screen",
  predictor_columns = c("study", "lang_group", "age_group", "percent_dominant", "trial_type", "trial_number", "dom_test"),
  summarize_by = "part_id"
) %>%
  group_by(part_id) %>%
  mutate(N_test = n()) %>%
  ungroup() %>%
  # keep only participants with data on all four trials
  filter(N_test == 4) %>%
  clean_names() %>%
  mutate(
    looking_time = samples_in_aoi / 60,
    log_looking = log(looking_time),
    # log(0) is minus infinity, so in this case use very very very small number
    log_looking = ifelse(looking_time == 0, log(0.0000001), log_looking)
  )


response_window_agg_by_sub_dominance_log <- response_window_agg_by_sub_dominance %>%
  select(part_id:trial_type, dom_test, log_looking) %>%
  pivot_wider(names_from = c(trial_type), values_from = log_looking) %>%
  mutate(diff_LT = switch - same)
```
### how many participants in this analysis?
```{r}
response_window_agg_by_sub_dominance_log %>%
  distinct(part_id, .keep_all = T) %>%
  group_by(study, age_group, lang_group) %>%
  count() %>%
  pivot_wider(names_from = lang_group, values_from = n)
```
### calculate anova
```{r}
anova_switch_LP_5mo <- response_window_agg_by_sub_dominance_log %>%
  filter(age_group == 5, study == "LP") %>%
  ezANOVA(
    dv = diff_LT,
    wid = part_id,
    within = dom_test,
    between = lang_group,
    return_aov = TRUE
  )

anova_switch_LP_12mo <- response_window_agg_by_sub_dominance_log %>%
  filter(age_group == 12, study == "LP") %>%
  ezANOVA(
    dv = diff_LT,
    wid = part_id,
    within = dom_test,
    between = lang_group,
    return_aov = TRUE
  )
anova_switch_FP_12mo <- response_window_agg_by_sub_dominance_log %>%
  filter(age_group == 12, study == "FP") %>%
  ezANOVA(
    dv = diff_LT,
    wid = part_id,
    within = dom_test,
    between = lang_group,
    return_aov = TRUE
  )

anova_switch_FP_18mo <- response_window_agg_by_sub_dominance_log %>%
  filter(age_group == 18, study == "FP") %>%
  ezANOVA(
    dv = diff_LT,
    wid = part_id,
    within = dom_test,
    between = lang_group,
    return_aov = TRUE
  )

# convert to suitable in-text output
anova_switch_LP_5mo_text <- convert_anova_to_apa_text(anova_switch_LP_5mo)
anova_switch_LP_12mo_text <- convert_anova_to_apa_text(anova_switch_LP_12mo)
anova_switch_FP_12mo_text <- convert_anova_to_apa_text(anova_switch_FP_12mo)
anova_switch_FP_18mo_text <- convert_anova_to_apa_text(anova_switch_FP_18mo)
```
### robustness test
```{r}
response_window_agg_by_sub_dominance_wide <- response_window_agg_by_sub_dominance %>%
  select(part_id:trial_type, dom_test, looking_time) %>%
  pivot_wider(names_from = c(trial_type), values_from = looking_time) %>%
  mutate(diff_LT = switch - same)

anova_switch_LP_5mo_robust <- response_window_agg_by_sub_dominance_wide %>%
  filter(age_group == 5, study == "LP") %>%
  ezANOVA(
    dv = diff_LT,
    wid = part_id,
    within = dom_test,
    between = lang_group,
    return_aov = TRUE
  )

anova_switch_LP_12mo_robust <- response_window_agg_by_sub_dominance_wide %>%
  filter(age_group == 12, study == "LP") %>%
  ezANOVA(
    dv = diff_LT,
    wid = part_id,
    within = dom_test,
    between = lang_group,
    return_aov = TRUE
  )
anova_switch_FP_12mo_robust <- response_window_agg_by_sub_dominance_wide %>%
  filter(age_group == 12, study == "FP") %>%
  ezANOVA(
    dv = diff_LT,
    wid = part_id,
    within = dom_test,
    between = lang_group,
    return_aov = TRUE
  )

anova_switch_FP_18mo_robust <- response_window_agg_by_sub_dominance_wide %>%
  filter(age_group == 18, study == "FP") %>%
  ezANOVA(
    dv = diff_LT,
    wid = part_id,
    within = dom_test,
    between = lang_group,
    return_aov = TRUE
  )

# convert to suitable in-text output
anova_switch_LP_5mo_text_robust <- convert_anova_to_apa_text(anova_switch_LP_5mo_robust)
anova_switch_LP_12mo_text_robust <- convert_anova_to_apa_text(anova_switch_LP_12mo_robust)
anova_switch_FP_12mo_text_robust <- convert_anova_to_apa_text(anova_switch_FP_12mo_robust)
anova_switch_FP_18mo_text_robust <- convert_anova_to_apa_text(anova_switch_FP_18mo_robust)
```
### results
```{r}
aov_LP_05mo_switch <- full_join(
  enframe(anova_switch_LP_5mo_text) %>% unnest(cols = c(value)) %>% rename(trans = value),
  enframe(anova_switch_LP_5mo_text_robust) %>% unnest(cols = c(value)) %>% rename(untrans = value)
) %>%
  mutate(sorting_variable = nchar(name), group = "LP_05mo") %>%
  arrange(sorting_variable)

aov_LP_12mo_switch <- full_join(
  enframe(anova_switch_LP_12mo_text) %>% unnest(cols = c(value)) %>% rename(trans = value),
  enframe(anova_switch_LP_12mo_text_robust) %>% unnest(cols = c(value)) %>% rename(untrans = value)
) %>%
  mutate(sorting_variable = nchar(name), group = "LP_12mo") %>%
  arrange(sorting_variable)

aov_FP_12mo_switch <- full_join(
  enframe(anova_switch_FP_12mo_text) %>% unnest(cols = c(value)) %>% rename(trans = value),
  enframe(anova_switch_FP_12mo_text_robust) %>% unnest(cols = c(value)) %>% rename(untrans = value)
) %>%
  mutate(sorting_variable = nchar(name), group = "FP_12mo") %>%
  arrange(sorting_variable)

aov_FP_18mo_switch <- full_join(
  enframe(anova_switch_FP_18mo_text) %>% unnest(cols = c(value)) %>% rename(trans = value),
  enframe(anova_switch_FP_18mo_text_robust) %>% unnest(cols = c(value)) %>% rename(untrans = value)
) %>%
  mutate(sorting_variable = nchar(name), group = "FP_18mo") %>%
  arrange(sorting_variable)


combined_switch_anova_results <- rbind(aov_LP_05mo_switch, aov_LP_12mo_switch, aov_FP_12mo_switch, aov_FP_18mo_switch) %>% as_tibble()
```









### plot interaction with direction of switch 
```{r}
response_window_agg_by_sub_dominance_wide %>%
  ggplot(., aes(x = lang_group, y = diff_LT, fill = dom_test)) +
  geom_hline(yintercept = 0, alpha = .3, size = .1) +
  geom_boxplot(width = .8, alpha = .7, fatten = NULL) +
  stat_summary(
    fun.data = "mean_se", geom = "pointrange", show.legend = F,
    position = position_dodge(.8)
  ) +
  facet_wrap(vars(study, age_group),
    ncol = 4,
    labeller = labeller(age_group = c("5" = "5-month-olds", "12" = "12-month-olds", "18" = "18-months-olds"))
  ) +
  scale_x_discrete(name = "Language Group") +
  scale_y_continuous(name = "Difference Score (Switch-Same)") +
  scale_fill_brewer(palette = "Dark2", name = "Direction of Switch", labels = c("into dominant", "into non-dominant")) +
  theme_apa() +
  theme(legend.position = "bottom")

ggsave(here("output", "figures", "FP_direction_of_switch_box_only.pdf"), height = 5, width = 10)
```
