---
appendix: Supplemental.Rmd
output: word_document

---
Supplementary materials for Manuscript _Keeping track of language_
written by Esther Schott
```{r}

```

```{r library, include=FALSE}
# load all required libraries using the groundhog package (installs libraries that are not installed yet)

packages_used <- c(
  "rmarkdown", "codebook", "labelled", "devtools",
  "pander", "knitr", "forcats", "beepr",
  "anytime", "apaTables", "arsenal", "broom", "diffdf", "dplyr", "data.table",
  "eyetrackingR", "ez", "forcats", "ggbeeswarm", "ggplot2", "glue",
  "here", "janitor", "lme4", "lubridate", "magrittr",
  "Matrix", "PupillometryR", "purrr", "RColorBrewer",
  "readr", "readxl", "rio", "rlang", "stringr", "tibble",
  "tidyr", "tidylog", "TOSTER", "zoo"
)
for (i in packages_used) {
  library(i, character.only = T)
}
library(papaja)
library(introdataviz)
library(rempsyc)
knit(here("scripts", "lpfp_eyemovement_analysis.Rmd"))
```

# Supplemental Materials

## Participant groups where recruitment was stopped

These participants included 3 9-month-olds (all bilinguals),  37 18-month-olds (9 bilingual, 17 monolingual, 11 who did not fit the criteria for either bi- or monolingual), as well as bilinguals with English or French and another language: 15 bilingual-other 5-months-olds and 9 bilingual-other 12-month-olds. 


## robustness analysis ANOVA
Table S1
```{r}

robust_anova <- all %>%
  select(name, robust, group) %>%
  nice_table() %>%
  save_as_docx(path = here("output", "tables", "TableS1_anova.docx"))
```

## equivalence test
Table S2
```{r}
eq_tests

eq_tests[, c(1:2, 4)] %>%
  nice_table() %>%
  save_as_docx(path = here("output", "tables", "TableS2_equivalence.docx"))
```

## correlation exposure to domiannt langauge
Table S3
```{r}
correlation_dominant_language %>%
  select(-log_transformed) %>%
  separate(untransformed, into = c(
    "r", "CI_1", "CI_2", "t_test",
    "p"
  ), sep = ",") %>%
  mutate(
    CI = paste(CI_1, CI_2, sep = ", "),
    t_test = paste(t_test, p, sep = ", ")
  ) %>%
  select(analysis_type, r, CI, t_test) %>%
  nice_table() %>%
  save_as_docx(path = here("output", "tables", "TableS3_correlation.docx"))
```
## correlation langauge mixing 
```{r}
correlation_lang_mix %>%
  select(-log_transformed) %>%
  separate(untransformed, into = c(
    "r", "CI_1", "CI_2", "t_test",
    "p"
  ), sep = ",") %>%
  mutate(
    CI = paste(CI_1, CI_2, sep = ", "),
    t_test = paste(t_test, p, sep = ", ")
  ) %>%
  select(analysis_type, r, CI, t_test) %>%
  nice_table() %>%
  save_as_docx(path = here("output", "tables", "TableS4_correlation_lang_mix.docx"))
```



## direction of switch
Table S4
```{r}

combined_switch_anova_results %>%
  select(-trans) %>%
  select(-sorting_variable) %>%
  nice_table() %>%
  save_as_docx(path = here("output", "tables", "TableS5_switch_anova.docx"))
```
